---
title: "Day_One_Session2"
author: "Allie Cole"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

### Logs and Exponents in R

Some examples of how to use 'log()' function and 'exp()' function in R

```{r}
#Examples of logs 

log(4)

#Examples of exponents 
exp(1.3862)

log(exp(1)) #think about in words what you are asking it to do. To what power do i have to raise e to get a value of e^1 (exp(1))

```

### Creating Sequences of Values 

```{r}
# A sequences from 1-20 by increments of 1 

ex_1 <- seq(from = 1, to = 20, by = 1)

#Vector from 0 to 40 by 0.2 
ex_2 <- seq(from = 0, to = 40, by = 0.2)

#Vector from 1 to 5000 by 10 
ex_3 <- seq(from = 1, to = 5000, by = 10)

```


### Create a Function for Logistic Growth 

Given the carrying capacity, the initial population and the growth rate, and a time, use the logistic growth model to estimate the population at that time

P = K / 1 + (K-P0/P0)e^rt

```{r}
pop_logistic <- function(capacity, init_pop, g_rate, time_yr) {
  
  capacity/ (1+ ((capacity - init_pop) / init_pop) * exp(-g_rate*time_yr))
  
}

pop_logistic(capacity = 2580, init_pop = 230, g_rate = 0.32, time_yr = 2.4)

```

### Try Finding Population over a Sequence of Times

```{r}
time_vec <- seq(from = 0, to = 15, by = 0.5) #vector of time from 0 to 20 that goes by increments of 0.5 years 

```

Now we have to estimate the pop over that time but with the same parameters we used above, capacity = 2580, init_pop = 230, g_rate = 0.32, but now with our time vector and not a single value. 

```{r}
chipmunk_pop <- pop_logistic(capacity = 2580, init_pop = 230, g_rate = 0.32, time_yr = time_vec)

```


### Cretae a Data Frame and Plot Chipmunk Population over time 

```{r}
chipmunk_df <- data.frame(time_vec, chipmunk_pop)

```


### Bare Minimum ggplot Graph 

```{r}
ggplot(data = chipmunk_df, aes(x = time_vec, y = chipmunk_pop)) + 
  geom_point() +
  labs(x = "Time (years)", 
       y = "Chipmunk Population (individuals)", 
       title = "Inyo NF chipmunks")
```












